The \frb\ Campaign: A Multi-Telescope Burst Detection and Implications for the FRB Population

### 2017-04-13 repeater-vladata.tex
draft ready for circulation

\begin{abstract}
We present results of the coordinated observing campaign that made the first arcsecond localization of a Fast Radio Burst, FRB 121102. Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories, of which one was detected by the Arecibo Observatory at 1.4~GHz. We use multi-observatory detection and constraints with modeling of bursts only seen at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law. We characterize burst spectra with a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg. The dispersion measure apparently changes significantly between bursts, which suggests that bursts have spectral structure that randomly biases the estimate of DM by as much as 5 pc cm$^{-3}$. We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1. This rate is broadly consistent with models of FRBs from young magnetars or pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
\end{abstract}

@@

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}. Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0.1\arcsec. Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec\ \citep[$\sim40$\ pc]{EVN}.

\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance. Its lookback and luminosity distances are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}. This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}. If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies. Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the first FRB detection.

@@

\section{Observations}
\label{sec:obs}
\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{timeline0}

@@

The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA. We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:sched}. Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.

@@

@@

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} and \citet{2015ApJ...807...16L}.}. Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}. Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration. A flux scale was calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.

@@

Four of the VLA bursts were observed simultaneously with either Arecibo, Effelsberg, or AMI-LA, and two were observed simultaneously with all four observatories (Figure \ref{fig:sched}). Of these bursts, only one VLA burst (on 17 Sep 2016) was simultaneously detected by another observatory (Arecibo).

Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets. We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from the top of the VLA and Arecibo bands, respectively. We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo data.

@@

**integrated flux is assuming 5 ms width!**

**confirm arecibo integrated flux and sensitivity**

Figure \ref{fig:multi} shows spectra built from integrated flux densities measured (or limited) during three burst with multi-telescope observing coverage. The burst on 17 Sep 2016 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively. The VLA integration time of 5~ms underresolves the pulse and the true integrated flux density would be 280 mJy for an assumed pulse width of 2~ms.
% correct the followign for estimated integrated flux
Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<0.6$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the bursts with simultaneous observing coverage are not consistent with a power law model for the burst spectra. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4/3}>+3.7$, while at Effelsberg the flux limits require $\alpha_{3/4.5}<-0.4$. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on 18 Sep 2016, which shows that a power law model is inappropriate even for a single burst.
% could note that these limits are understated by VLA integrated flux underestimate

\begin{figure}[htb]
\begin{center}
 \includegraphics[width=\columnwidth]{multispec.png}
 \caption{Broadband spectra for three bursts of \frb\ with simultaneous multi-telescope observing coverage. Measurements are shown with dots and upper limits with triangles. Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold. Overlapping points are offset by a few tens of MHz in frequency for visualization.
 \label{fig:multi}}
\end{center}
\end{figure}

@@

To better understand the spectra, we used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency). We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square pulse of temporal width. We use a log likelihood function $\ln \mathcal{L}=(-1/2)\ \sum_i (S_i - S_{i, \rm{model}})^2/\sigma_s^2$, where $S_i$\ refers to the measured and modeled flux density in a single pixel of the dynamic spectrum and $\sigma_s\approx 70\ \mu$Jy is the measured off-burst noise per 5~ms integration and 4~MHz channel. A flat prior was used over all ranges with valid data with the requirement that the integrated signal must have a detection significance higher than 8$\sigma$. The 6-dimensional models were sampled with 100 chains taking 700 steps; we ignored the first 200 steps to properly sample the posterior distributions.

**discuss goodness of fit?**
... The inter-channel modulation was ignored in the model...

@@

This analysis differs from traditional analysis in that it simultaneously models the spectral and temporal evolution of the burst. A typical \frb\ burst takes $\sim180$~ms or 36 integrations to cross the observing band from 2.5 to 3.5~GHz. The effect of a finite pulse width is visible as the burst moves from one integration to the next, even for widths narrower than the integration time of 5~ms. Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm1$~ms (95\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band. The brightest burst (57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its burst arrival time is measured with a precision of $\sim50\mu$s. Note that these errors are only accurate to the degree that the model represents the data. One potential bias in the model is that we do not model scintillation effects.

@@

The top panel of Figure \ref{fig:dmmodel} shows the 68\% confidence intervals on the DM for all nine VLA bursts as a function of burst time. The burst DMs are not consistent with any single value and tend to be larger than the long-term average of 560.5 pc cm$^{-3}$. The range and variance in DM observed by the VLA is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}. As noted before, this is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts. The VLA data demonstrate that the burst-dependent DM effect is visible at frequencies near 3~GHz. Assuming a ``true'' DM of 560.5 pc cm$^{-3}$, the excess DM can be interpreted as a frequency-dependent delay that varies between bursts with a delay rate up to 2~ms GHz$^{-1}$ or an effective DM of $\sim5$~pc cm$^{-3}$.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\columnwidth]{burst_dmdt}
\caption{(Top) Burst time versus DM for nine 3~GHz bursts detected by the VLA. The 68\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz. (Bottom) Temporal width versus burst DM for the same nine VLA bursts.
\label{fig:dmmodel}}
\end{center}
\end{figure}

@@

We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz. The flux density of the Arecibo burst detected on MJD 57648 is an order of magntude less than that seen by the VLA. At the same time, three other bursts from \frb\ had similar observing coverage but were not detected simultaneously. This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz. The center frequency of this envelope varies from burst to burst with no obvious pattern.

If \frb\ burst spectra are typical of the larger FRB population, then population models need to be generalized beyond the assumption of a spectral power law. Most obviously, \frb\ implies that future multi-telescope searches for bursts are unlikely to simultaneously detect bursts in different bands. Second, since burst spectra have limited bands, the burst detection rate at one frequency may not represent that at another. That will require rate estimates for the FRB population to be made explicitly frequency-dependent. Finally, we note that the odds of detecting a burst will improve with bandwidth beyond the gain in sensitivity, since bandwidths wider than the FRB characteristic width can find otherwise undetectable bursts. However, this does require that FRB search algorithms search for bursts with a width equal to the characteristic width.

After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift. This drift can be interpreted as an excess DM of roughly 5 pc cm$^{-3}$. We also measure a burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts of a similar scale. This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen up to 3~GHz. The simultaneous VLA/Arecibo burst also shows that this excess is evident in an individual burst at 1.2 to 3.5~GHz.

**How to use Hessels et al results on sub bursts and DM?**

These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}. That work uses bright, coherently-dedispersed bursts to identify sub-bursts that preferentially drift to lower frequencies at later times. With high-resolution dynamic spectra, one can define a heuristic that distinguishes between a burst-specific dispersion-like effect and a more stable (``true'') dispersion. Since the sub-bursts tend to drift to lower frequencies, they systematically bias DM measurements made with low-resolution data (like the VLA and earlier Arecibo and GBT obsrevaitons). Interestingly, our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width. This could be a signature of blending of many unresovled sub-bursts in a single VLA burst spectrum.

@@

We now know that \frb\ is detectable with the VLA out to $z=0.7$, which suggests that cosmological effects are even more important for understanding properites of the FRB population. \citet{2017arXiv170208040C} demonstrate how redshift space distortions, time dilation, and spectral index (``k-correction'') effects can flatten the flux distribution. To this complex scene, we add the fact that \frb\ burst spectra are not defined by a spectral index, which suggests that k-corrections are likely to be very difficult to calculate in practice. Rather than using wide band burst spectra to measure a single spectral index, we now must measure the burst rate as a function of frequency. These need to be measured at similar times to ensure they represent a similar state of the FRB.

**how to include new result on freq-dependent burst rate?**

If we assume \frb\ is representative of the FRB population, we can estimate this frequency-dependent burst rate. The VLA and Arecibo observed intensively in a coordinated fashion during the late-2016 campaign. 
A complete search for bursts from the Arecibo is ongoing, but early results suggest that the burst rate at a fixed energy is much higher at 1.4~GHz than at 3~GHz. 
This suggests that high-redshift FRBs will have an apparently lower rate that flattens the $dN/dF$\ distribution in a manner similar to a k-correction. We can only infer the presence of this effect for observations near 1.4~GHz, since we have no estimate of the \frb\ burst rate outside the frequency range from 1.4 to 3~GHz in the observed frame. Propagation effects suggest that the rate will be lower at sub-GHz frequencies \citep{2017MNRAS.465.2286R, 2017arXiv170107457C}. If so, the tension between constraints on $\alpha$\ near 800~MHz and 1.4~GHz may be resolved by a frequency-dependent FRB rate that peaks near 1.4~GHz.

@@

**correct for time dilation?**

@@

Here, we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class and recasting it as a volumetric rate of FRB sources (i.e., a birth rate). The volumetric rate of FRB sources is $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$. The newest estimates of the projected FRB rate are lower by a factor of 5 \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}. There is relatively little constraint on the beaming factor, but Galactic pulsars have values on the order of 10\% \citep{1998MNRAS.298..625T}.

\frb\ has an absolute energy scale that can be used to convert the observation-dependent fluence limit into a FRB horizon scale. At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a survey with a fluence limit of 1~Jy~ms can detect \frb\ at $z\approx1$. The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but that likely overestimates distance since DM is expected to have significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
%For reference, we note that cosmic star formation rate peaks between redshift of 2 and 3\citep{2014ARA&A..52..415M}.

>>>>

\begin{abstract}
We present results of the coordinated observing campaign that made the first arcsecond localization of a Fast Radio Burst, FRB 121102. Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories, of which one was detected by the Arecibo Observatory at 1.4~GHz. We use multi-observatory constraints and modeling of bursts only seen at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law. We characterize burst spectra with a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg. The dispersion measure apparently changes significantly between bursts, which suggests that bursts have frequency-dependent profiles that randomly bias the estimate of DM by up to 1\%. We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1. This rate is broadly consistent with models of FRBs from young magnetars or pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
\end{abstract}

@@

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out 
cataclymic models for this source \citep{2016Natur.531..202S}. The typical DM measured by early Arecibo Observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher value have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).

Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0.1\arcsec. Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec, four orders of magnitude better than any other FRB \citep[$\sim40$\ pc]{EVN}. The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}. At this distance, \frb\ is orders of magnitude more luminous than any other millisecond transient. If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies. Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the first FRB detection.

@@

\section{Observations}
\label{sec:obs}

\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{timeline0}

@@

The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA. We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}. Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.

@@

\begin{table*}
\tiny
\caption{Table of Observations}
\centering
\begin{tabular}{lcccccc}
Day & Start time & Duration & Band & VLA Detections & Coverage & Detections \\
(yyyy-mm-dd) & (hh:mm:ss) & (minutes) & & & &  \\ \hline
2015-11-25 & 3:25:29 & 60 & L & 0 &  & \\
2015-12-01 & 5:31:31 & 60 & L & 0 &  &  \\
2015-12-03 & 2:53:57 & 60 & L & 0 &  &  \\
2015-12-05 & 4:45:44 & 60 & L & 0 &  &  \\
2015-12-07 & 4:37:50 & 60 & L & 0 &  &  \\
2015-12-09 & 9:29:25 & 60 & L & 0 &  &  \\
2015-12-11 & 9:22:27 & 60 & L & 0 &  &  \\
2015-12-13 & 9:13:7 & 60 & L & 0 &  &  \\
2015-12-15 & 9:6:16 & 60 & L & 0 &  &  \\
2015-12-17 & 8:57:51 & 60 & L & 0 &  &  \\
2016-04-25 & 15:39:33 & 42 & S & 0 &  &  \\
2016-04-26 & 21:49:35 & 15 & S & 0 &  &  \\
2016-04-30 & 19:14:46 & 60 & S & 0 &  &  \\
2016-05-01 & 18:8:21 & 60 & S & 0 &  &  \\
2016-05-03 & 22:53:26 & 60 & S & 0 &  &  \\
2016-05-04 & 22:50:30 & 60 & S & 0 &  &  \\
2016-05-06 & 18:25:12 & 60 & S & 0 &  &  \\
2016-05-07 & 19:34:13 & 60 & S & 0 &  &  \\
2016-05-08 & 19:30:20 & 60 & S & 0 &  &  \\
2016-05-13 & 17:12:48 & 135 & S & 0 &  &  \\
2016-05-14 & 17:14:11 & 135 & S & 0 &  &  \\
2016-05-15 & 17:15:26 & 135 & S & 0 &  &  \\
2016-05-16 & 16:59:52 & 135 & S & 0 &  &  \\
2016-05-20 & 16:45:46 & 135 & S & 0 &  &  \\
2016-05-21 & 16:44:6 & 135 & S & 0 &  &  \\
2016-05-22 & 16:43:53 & 135 & S & 0 &  &  \\
2016-05-23 & 16:44:11 & 135 & S & 0 &  &  \\
2016-05-27 & 16:29:34 & 135 & S & 0 &  &  \\
2016-08-23 & 17:26:28 & 54 & S & 1 &  &  \\
2016-09-02 & 15:52:17 & 54 & S & 2 &  &  \\
2016-09-07 & 10:14:50 & 120 & S & 1 &  &  \\
2016-09-08 & 10:14:40 & 120 & S & 0 &  &  \\
2016-09-10 & 9:59:36 & 120 & S & 0 &  &  \\
2016-09-11 & 9:59:49 & 120 & S & 0 &  &  \\
2016-09-12 & 9:15:19 & 120 & S & 1 & AMI-LA &  \\
2016-09-13 & 9:23:59 & 120 & S & 0 &  &  \\
2016-09-14 & 9:20:23 & 120 & S & 1 & Arecibo,AMI-LA &  \\
2016-09-15 & 9:16:29 & 120 & S & 1 &  &  \\
2016-09-16 & 9:11:23 & 120 & S & 0 &  &  \\
2016-09-17 & 8:59:20 & 120 & S & 1 & Arecibo,Effelsberg,AMI-LA & Arecibo \\
2016-09-18 & 8:59:27 & 120 & S & 1 & Arecibo,Effelsberg,AMI-LA &  \\
2016-09-19 & 8:44:32 & 120 & S & 0 &  &  \\
2016-09-20 & 8:44:33 & 120 & S & 0 &  &  \\
2016-09-20 & 17:19:3 & 120 & C & 0 &  &  \\
2016-09-21 & 9:13:57 & 120 & C & 0 &  &  \\
2016-09-22 & 9:12:24 & 120 & C & 0 &  &  \\
\end{tabular}
%\tablenotetext{a}{}
\label{tab:obs}
\end{table*}

@@

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} and \citet{2015ApJ...807...16L}.}. Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$. Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration. A flux scale was calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.

@@

Four of the VLA bursts were observed simultaneously with either Arecibo, Effelsberg, or AMI-LA, and two were observed simultaneously with all four observatories (Figure \ref{fig:sched}). Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).

Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets. We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively. We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo at the time of observation.

@@

Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for three burst with multi-telescope observing coverage. The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively. Here we assume a typical pulse width of 2~ms to measure VLA and Arecibo integrated flux densities of 278 and 64 mJy at 3 and 1.4~GHz, respectively. Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=1.9$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the bursts with simultaneous observing coverage are not consistent with a power law model for the burst spectra. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4/3}>+4.8$, while at Effelsberg the flux limits require $\alpha_{3/4.5}<-2.7$. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.
% could note that these limits are understated by VLA integrated flux underestimate

\begin{figure}[htb]
\begin{center}
 \includegraphics[width=\columnwidth]{multispec.png}
 \caption{Broadband spectra for three bursts of \frb\ with simultaneous multi-telescope observing coverage. Measurements are shown with dots and upper limits with triangles. Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold. Overlapping points are offset by tens of MHz in frequency for visualization.
 \label{fig:multi}}
\end{center}
\end{figure}

@@

We used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency). We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square pulse of temporal width. The inter-channel amplitude modulation was ignored in the model.

We use a log likelihood function $\ln \mathcal{L}=(-1/2)\ \sum_i (S_i - S_{i, \rm{model}})^2/\sigma_s^2$, where $S_i$\ refers to the measured and modeled flux density in a single pixel of the dynamic spectrum and $\sigma_s\approx 70\ \mu$Jy is the measured off-burst noise per 5~ms integration and 4~MHz channel. A flat prior was used over all ranges with valid data with the requirement that the integrated signal must have a detection significance higher than 8$\sigma$. The 6-dimensional models were sampled with 100 chains taking 700 steps; we ignored the first 200 steps to properly sample the posterior distributions.

@@

This analysis differs from traditional analysis in that it simultaneously models the spectral and temporal evolution of the burst. A typical \frb\ burst takes $\sim180$~ms or 36 integrations to cross the observing band from 2.5 to 3.5~GHz. The effect of a finite pulse width is visible as the burst moves from one integration to the next, even for widths narrower than the integration time of 5~ms. Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm0.5$~ms (68\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band. The brightest burst (57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its burst arrival time is measured with a precision of $\sim50\mu$s. Note that these errors are only accurate to the degree that the model represents the data. One potential bias in the model is that we do not model scintillation effects.

@@

Figure \ref{fig:dmmodel} compares the 68\% confidence intervals on the DM for all nine VLA bursts against detection time (top panel) and the modeled burst temporal width (bottom panel). The error weighted mean burst DM is 567.8$\pm$0.1 pc cm$^{-3}$, significantly larger than the long-term average of 560.5 pc cm$^{-3}$ seen by Arecibo during this campaign. However, we note that the 95\% confidence intervals in DM for multiple bursts are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM. The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
%As noted before, this is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\columnwidth]{burst_dmdt}
\caption{(Top) Burst time versus DM for nine 3~GHz bursts detected by the VLA. The DM scale for both panels is shown at the bottom. The 68\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred from Arecibo observations at 1.4~GHz (Hessels et al, in prep). (Bottom) Temporal width versus burst DM for the same nine VLA bursts.
\label{fig:dmmodel}}
\end{center}
\end{figure}

@@

We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz. The flux density of the Arecibo burst detected on MJD 57648 is an order of magntude less than that seen by the VLA. At the same time, three other bursts from \frb\ had similar observing coverage but were not detected simultaneously. This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz. This confirms earlier results at 1.4~GHz \citep{2016Natur.531..202S,2016arXiv160308880S} with a wider bandwidth and extends the presence of this phenomenon to 3~GHz.

If \frb\ burst spectra are typical of the larger FRB population, then population models need to be generalized beyond the assumption of a spectral power law. Most obviously, \frb\ implies that future multi-telescope searches for bursts are unlikely to simultaneously detect bursts in different bands. Second, since burst spectra have limited bands, the burst detection rate at one frequency may not represent that at another. Rate estimates for the FRB population will need to explicitly account for the frequency-dependent rate. Finally, we note that the odds of detecting a burst will improve with bandwidth beyond the gain in sensitivity, since bandwidths wider than the FRB characteristic width are more likley to cover the burst envelope. However, this does require that FRB search algorithms search for bursts with a width equal to the characteristic width.

After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift. This drift can be interpreted as an excess DM, but contemporaneous observations at 1.4~GHz measured a significantly lower DM (560.5 pc cm$^{-3}$; Hessels et al, in prep). This excess DM is comparable to the burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts. This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen up to 3~GHz.

One interpretation for the burst-dependent DM is that the bursts have a frequency-dependent pulse shape. Pulsar pulse shapes evolve with frequency on GHz frequency scales, presumably due to changes in the beam shape \citep{1988MNRAS.234..477L}. The burst-dependent DM changes are on the order of 1\% of the total DM (equivalent to a delay rate up to 2~ms GHz$^{-1}$), which is much larger than typically observed \citep{2017MNRAS.466.3706L}. The systematic offset of the VLA 3~GHz DM from that observed by Arecibo suggests that any such burst frequency evolution must be larger at higher frequencies. Our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width. This could be a signature unresovled spectrotemporal structure in the VLA burst spectra that biases the measured DM.

@@

We now know that \frb\ is detectable with the VLA out to $z=0.7$, which suggests that cosmological effects are even more important for understanding properites of the FRB population. \citet{2017arXiv170208040C} demonstrate how redshift space distortions, time dilation, and spectral index (``k-correction'') effects can flatten the flux distribution. To this complex scene, we add the fact that \frb\ burst spectra are not defined by a spectral index, which suggests that k-corrections are likely to be very difficult to calculate in practice. If the FRB burst rate is higher at low (rest) radio frequencies, then high-redshift FRBs will have an lower (redshifted) rate that flattens the $dN/dF$\ distribution in a manner similar to a k-correction. However, propagation effects are expected to suppress the FRB rate at sub-GHz frequencies \citep{2017MNRAS.465.2286R, 2017arXiv170107457C} as well. The VLA and Arecibo observed intensively in a coordinated fashion during the late-2016 campaign and a comparison of their relative rates will be presented elsewhere.

@@

@@

Here, we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class and recasting it as a volumetric rate of FRB sources (i.e., a birth rate). Crudely, the volumetric rate of FRB sources can be defined as $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$. The newest estimates of the projected FRB rate are $2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms \citep{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}. There is relatively little constraint on the beaming factor, but Galactic pulsars have beaming solid angle fractions on the order of 10\% \citep{1998MNRAS.298..625T}.

\frb\ has an absolute energy scale that can be used to estimate a horizon scale for the typical FRB survey sensitivity. At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a survey with a fluence limit of 1~Jy~ms can detect \frb\ at $z\approx1$. The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but that likely overestimates distance since DM is expected to have significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
%For reference, we note that cosmic star formation rate peaks between redshift of 2 and 3\citep{2014ARA&A..52..415M}.
